>

### 2019-11-18 manuscript/manuscript.Rmd
JT edits

The United States and other developed nations face an epidemic of obesity and
chronic diseases, including cardiovascular diseases, chronic respiratory
diseases, diabetes, stroke, joint and bone diseases, and cancer. These diseseases
can severely limit the lifespan of affected individuals [@WHO2014], with 
substantial financial costs for treatment borne both privately and socially
[@Finkelstein2009]. Though a moderate amount of regular physical activity
has been established as an effective strategy for reducing and managing obesity
and many of the aforementioned chronic diseases [@CDC2009; @Durstine2013],
a large portion of U.S. adults do not participate in sufficient physical
activity [@Wolf2008].

Historically, most large-scale health promotion efforts focused on
individual-level interventions intended to educate people about healthy
lifestyles and behaviors, touching on topics including diet and exercise.
Over the last several years a new *social* model of health has evolved,
described by @Duhl1999 
``as an outcome of the effects of socioeconomic status, culture,
environmental conditions, housing, employment and community influences''[-@Duhl1999, p.7].
In this new paradigm, resources provided via civil infrastructure --- in
particular parks and other public green spaces --- play a crucial role in
promoting and sustaining public health [@Bedimo-Rung2005; @Wells2007; @Coutts2008].
After all, it does little to lecture individuals on the importance of exercise
if their community is built in such a way that such exercise is expensive,
unenjoyable, or unsafe.

In spite of the potential for green spaces to influence public health outcomes 
and numerous studies attempting to empirically estimate the strength of these
outcomes, evidence to date has been mixed. A major challenge researchers have
faced is a proliferation of techniques for measuring access to green spaces, of
which many are plausible but lack robust theoretical basis. In this
paper, we apply a holistic and flexible measurement for park accessibility
based in activity location choice theory. This utility-based accessibility measure
compares the continuous distance to all parks in the region, weighted against
the sizes of each park and its other assorted amenities.

We apply this measurement to study the link between park accessibility and
attractiveness and Census tract-level aggregate physical activity participation
and obesity rates in New York City, controlling for spatially correlated
unobserved effects, spatial spillovers of covariates, and tract-level
socioeconomic characteristics. We also demonstrate how the utility-based
accessibility metric can potentially be expanded to account for other measures
of a park's attractiveness including its observed social media activity and the
presence of various park amenities. The paper concludes with a discussion of
opportunities for future research.

@@

The large majority of extant research on the topic of park access and public health
outcomes has been involved with comparing metropolitan regions against each other. For example,
@West2012 used park data from
the Trust for Public Land’s 2010 "City Park Facts" and public health data from the
Behavioral Risk Factor Surveillance System (BRFSS) to examine the relationship
between the density of park land and physical activity and obesity rates for 67
metropolitan statistical areas in the U.S. The findings in this case conformed to 
expectation; that is, the study found a significant positive association
between park density and physical activity and a significant negative
association between park density and obesity.
@Larson2016 similarly used self-reported scores on the Gallup-Healthways
Wellbeing Index to evaluate the relationship between physical health and park
quantity, quality, and accessibility in 44 U.S. cities. While the authors found
positive associations between wellbeing and park quality and accessibility,
these relationships were not statistically significant.
Conversely, @Richardson2012 examined the relationship between total urban
greenspace and mortality rates for selected maladies; though the authors did not
find a statistically significant relationship between the quantity of urban
greenspace and mortality caused by lung cancer, diabetes, heart disease or car
accidents, they did find that all-cause mortality was --- oddly --- *higher* in greener
cities. Finally, in a meta-analysis of 20 peer reviewed journal articles exploring the
relationship between parks and objectively measured physical activity,
@Bancroft2015 found that five studies reported a significant positive
association between the two, six studies produced mixed results, and nine
studies found no association at all.

Metropolitan-level analyses such as those described above do not capture the
within-city variation in accessibility to parks that exist in many cities. Some
cities with large amounts of total greenspace may nevertheless unequally
distribute this space throughout the city, leading to areas with poor access.
Conversely, a city with a smaller overall proportion of greenspace may give all
of its citizens better access to sufficient greenspace to meet their needs or
wants for physical activity. Considering access at the neighborhood level within
a single city may also eliminate some regional or cultural fixed effects
affecting metropolitan-level analyses.

@@

@Kinnell2006 surveyed park users in New Jersey and applied a multinomial logit
model to determine which factors influence a park's perceived utility as a park
trip destination. By transferring estimates of common variables between our
data and this survey-based model, we can create a second utility specification
as
\begin{equation}\label{eq:u_multi}
\begin{split}
V_{ij} & = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \\ 
  & \quad \lambda_t * trails + \lambda_{c} * courts + \lambda_p * playgrounds
\end{split}
\end{equation}
with $\lambda_t = 0.99$, $\lambda_c = 0.43$, and $\lambda_p = 0.26$. Kinnell et al.\
did not transform their size and distance estimates, so we retain the previously 
estimated and applied values. We assume that the other covariates in the 
model which we do not have available to us (e.g., boat launches, picnic areas) are
orthogonal to the included parameters and leaving them out will not affect the
values of the included coefficients.

>>>>

The United States and other developed nations face an epidemic of obesity and
chronic diseases, including cardiovascular diseases, chronic respiratory
diseases, diabetes, stroke, joint and bone diseases, and cancer. These diseases
can severely limit the lifespan of affected individuals [@WHO2014], with 
substantial financial costs for treatment borne both privately and socially
[@Finkelstein2009]. Though a moderate amount of regular physical activity
has been established as an effective strategy for reducing and managing obesity
and many of the aforementioned chronic diseases [@CDC2009; @Durstine2013],
a large portion of U.S. adults do not participate in sufficient physical
activity [@Wolf2008].

Historically, most large-scale health promotion efforts focused on
individual-level interventions intended to educate people about healthy
lifestyles and behaviors, touching on topics including diet and exercise.
Over the last several years a new *social* model of health has evolved,
described by @Duhl1999 
``as an outcome of the effects of socioeconomic status, culture,
environmental conditions, housing, employment and community influences''[-@Duhl1999, p.7].
In this new paradigm, resources provided via civil infrastructure --- in
particular parks and other public green spaces --- play a crucial role in
promoting and sustaining public health [@Bedimo-Rung2005; @Wells2007; @Coutts2008].
After all, it does little to educate individuals on the importance of exercise
if their community is built in such a way that such exercise is expensive,
unenjoyable, or unsafe.

In spite of the potential for green spaces to influence public health outcomes 
and numerous studies attempting to empirically estimate the strength of these
outcomes, evidence to date has been mixed. A major challenge researchers have
faced is a proliferation of techniques for measuring access to green spaces, of
which many are plausible but lack robust theoretical bases. In this
paper, we apply a holistic and flexible measurement for park accessibility
based in activity location choice theory. This utility-based accessibility measure
compares the continuous distance to all parks in the region, weighted against
the sizes of each park and its other assorted amenities.

We apply this measurement to study the link between park accessibility and
attractiveness and census tract-level aggregate physical activity participation
and obesity rates in New York City, controlling for spatially correlated
unobserved effects, spatial spillovers of covariates, and tract-level
socioeconomic characteristics. We also demonstrate how the utility-based
accessibility metric can potentially be expanded to account for other measures
of a park's attractiveness including its observed social media activity and the
presence of various park amenities. The paper concludes with a discussion of
opportunities for future research.

@@

The large majority of extant research on the topic of park access and public health
outcomes has been focused on comparing metropolitan regions against each other.
For example, @West2012 used park data from
the Trust for Public Land’s 2010 "City Park Facts" and public health data from the
Behavioral Risk Factor Surveillance System (BRFSS) to examine the relationship
between the density of park land and physical activity and obesity rates for 67
metropolitan statistical areas in the U.S. The findings in this case conformed to 
expectation; that is, the study found a significant positive association
between park density and physical activity and a significant negative
association between park density and obesity.
@Larson2016 similarly used self-reported scores on the Gallup-Healthways
Wellbeing Index to evaluate the relationship between physical health and park
quantity, quality, and accessibility in 44 U.S. cities. While the authors found
positive associations between wellbeing and park quality and accessibility,
these relationships were not statistically significant.
Conversely, @Richardson2012 examined the relationship between total urban
greenspace and mortality rates for selected maladies; though the authors did not
find a statistically significant relationship between the quantity of urban
greenspace and mortality caused by lung cancer, diabetes, heart disease or car
accidents, they did find that all-cause mortality was --- oddly --- *higher* in greener
cities. Finally, in a meta-analysis of 20 peer reviewed journal articles exploring the
relationship between parks and objectively measured physical activity,
@Bancroft2015 found that five studies reported a significant positive
association between the two, six studies produced mixed results, and nine
studies found no association at all.

Metropolitan-level analyses such as those described above do not capture the
within-city variation in accessibility to parks that exist in many cities. Some
cities with large amounts of total greenspace may nevertheless unequally
distribute this space throughout the city, leading to areas with poor access.
Conversely, a city with a smaller overall proportion of greenspace may give all
of its citizens better access to sufficient greenspace to meet their needs or
desires for physical activity. Considering access at the neighborhood level within
a single city may also eliminate some regional or cultural fixed effects
affecting metropolitan-level analyses.

@@

@Kinnell2006 surveyed park users in New Jersey and applied a multinomial logit
model to determine which factors influence a park's perceived utility as a park
trip destination. By transferring estimates of common variables between our
data and this survey-based model, we can create a second utility specification
as
\begin{equation}\label{eq:u_multi}
\begin{split}
V_{ij} & = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij}) + \\ 
  & \quad \lambda_t * trails + \lambda_{c} * courts + \lambda_p * playgrounds
\end{split}
\end{equation}
with $\lambda_t = 0.99$, $\lambda_c = 0.43$, and $\lambda_p = 0.26$. Kinnell et
al. did not transform their size and distance estimates, so we retain the
previously estimated and applied values. We assume that the other covariates in
the model which we do not have available to us (e.g., boat launches, picnic
areas) are orthogonal to the included parameters and leaving them out will not
affect the values of the included coefficients.
